### 2014-11-25 reports/report.Rmd
Split apart baad to avoid report rebuilds
Depends only on the baad data, and less on other studies metadata.

```{r summary_table, results='asis', echo=FALSE}
# From the ms functions:
tab <- summary_table(data_study$data, baad$dictionary)
kable(tab[names(tab) != "Studies"], "markdown", align="l", padding=10)
```

@@

```{r variable_plots, fig.height=12, fig.width=12, echo=FALSE}
report_variable_plots(data_study, baad)
```

>>>>

```{r summary_table, results='asis', echo=FALSE}
# From the ms functions:
tab <- summary_table(data_study$data, baad_dictionary)
kable(tab[names(tab) != "Studies"], "markdown", align="l", padding=10)
```

@@

```{r variable_plots, fig.height=12, fig.width=12, echo=FALSE}
report_variable_plots(data_study, baad_data, baad_dictionary)
```
